 

### 2023-02-22 paper1.Rmd
Revising tables to improve readability
Addition of appendices, revisions throughout papers, acknowledgements

# Loading libraries
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(RColorBrewer)
library(sp)
library(broom)
library(sf)
library(scales)
library(viridis)
library(data.table)
library(ggpubr)
library(lemon)
library(rnaturalearth)
library(rnaturalearthdata)
library(sysfonts)
library(showtext)
font_add_google("Source Sans Pro")
library(gridExtra)
showtext_auto() 
showtext_opts(dpi = 300)

@@

# Import map data
world <- ne_countries(scale = "medium", returnclass = "sf")
world$iso_code <- world$gu_a3
world$iso_code[world$adm0_a3 == "SDS"] <- "SSD"

@@

data_rev$estimate_newlab <- factor(data_rev$estimate_newlab ,      # Reordering group factor levels
                                   levels = c("Original approach",
                                              "Reallocation approach",
                                              "PAF method",
                                              "Composite approach"))
# Merging map and dataframe
data_rev_map <- full_join(world, data_rev, by = "iso_code") %>% filter(numeric_name == "val")

@@

results_sentence1 <- paste0(
  "Under GBD 2019, over ",
  results1,
  " million DALYs were attributed to mental disorders, or roughly ",
  results2,
  "\\% of the global burden. After including alcohol and drug use, neurological disorders, chronic pain, suicide, and self-harm, the share due to mental disorders rose to ",
  results3,
  "\\% of global DALYs (approximately ",
  results4,
  " million DALYs). Under the composite approach, an additional  ",
  abstract1-results4,
  " million DALYs were attributed to mental disorders, encompassing, in total, over ",
  abstract2,
  "\\% of global DALYs. Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising ",
  ifelse(results5/results6 > 2.4, "over twice", ifelse(results5/results6> 2, "roughly twice", "approximately twice")),
  " the burden of disease in high-income countries compared to low-income countries.")

@@

With a third of disability-adjusted life years (DALYs) due to NCDs arising from mental disorders, this landmark paper estimated that the value of losses due to mental disorders was roughly 1.3 trillion USD in 2010 (1.6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion USD 2010 (or approximately 3.0 trillion USD in 2019) by 2030. (See Supplementary appendix Tables S1 and S2 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]

@@

The most recent estimates of morbidity and mortality due to mental disorders come from the Global Burden of Disease (GBD) 2019 study.[@vosGlobalBurden3692020a] The GBD study provides disease burden estimates using DALYs, years of life lost (YLLs), and years lived with disability (YLDs), which are then aggregated within a hierarchical grouping scheme that classifies causes of disability and death at different levels of mutually exclusive and completely exhaustive categories. (Mental disorders are a Level 2 condition, nested under NCDs; see Table S3.)

@@

@@

```
\addcontentsline{lot}{table}{Table 1.1: Comparison of the composition of the global burden of mental disorders, by estimation approach.}

@@

In addition to our base-case economic valuation, we further report our VSL estimates using three times GDP per capita as the value of a DALY. (Alternative valuations using values of $1,000 and $5,000, as well as purchasing power parity (PPP)-adjusted GDP per capita, are reported in Tables S5 and S6 of the Supplementary appendix.)

@@

\blandscape
```{r table1_2, echo = FALSE, include = TRUE, out.width = '100%'}

@@

```
\addcontentsline{lot}{table}{Table 1.2: Disability-adjusted life years (DALYs) attributable to mental disorders as totals (millions) and percentages of overall burden, by estimation approach.}

@@

Rates of DALYs and deaths attributable to mental disorders under the different estimation approaches are presented by GBD region (Figure \ref{figure_gbd_adjusted}). Geographically, the composite approach allocated a large portion of DALYs (to mental disorders) in Eastern Europe, North and Latin America, and sub-Saharan Africa. This is largely driven by the inclusion of premature mortality in the composite approach. Estimates of DALYs by country income group and GBD region are reported in Table 1.2. (Estimates of deaths are reported in Table S4-6.)

Under the three approaches, we calculated the economic value of mental disorder losses (Table 1.3). `r results_sentence2`. Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7.2 trillion international dollars in 2019 (Table S7).

@@

```{r figure_gbd_adjusted, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap="DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population.", out.extra='', fig.cap=paste("\\label{figure_gbd_adjusted}DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population. Values are aggregated by GBD region. DALYs: Disability-adjusted life years; YLDs: years lived with disability; YLLs: years of life lost; GBD: Global Burden of Disease.", sep=" "), fig.width = 11, fig.height = 11, fig.align='center', out.width = '97%'}

@@

j = 1
i = "ihme_region"
k = "rate_per_100k"
m = "abs"

@@

deaths <- data_rev_map %>% 
  filter(measure_id == j) %>% 
  filter(estimate_id %in%  c(1,2,4)) %>% 
  mutate(var_cut = cut(ihme_region_rate_per_100k, 
                       breaks =c(0, 1, 20, 40, 60, 80, 100, 120, 130, 140, max(temp$ihme_region_rate_per_100k)))) %>%
  ggplot() +
  geom_sf(mapping = aes(fill = var_cut), color = "grey95", size = 0.001) +
  geom_sf(data = . %>%   group_by(ihme_region) %>% 
            st_set_precision(1e4) %>%
            summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
  theme(panel.grid.major = element_blank(), 
        panel.background = element_blank(),
        axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        text = element_text(family = "Source Sans Pro")) + 
  labs(subtitle = "D: Deaths",
    fill=
      ifelse(j == 1,ifelse(k == "rate_per_100k", "Deaths", "% of deaths"),
             ifelse(j == 2, ifelse(k == "rate_per_100k", "DALYs", "% of DALYs"),
                    ifelse(j == 3, ifelse(k == "rate_per_100k", "YLDs", "% of YLDs"), 
                           ifelse(k == "rate_per_100k", "YLLs", "% of YLLs"))))) +
  scale_fill_manual(values=setNames(lancet_pal, levels(data_rev_map$var_cut))) +
  coord_sf(ndiscr = F) + 
  facet_grid(~estimate_newlab) +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 11),
        legend.text =  element_text(size = 10),
        plot.subtitle=element_text(size=15),
        text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")
        ,
        strip.text = element_text(size=14)
  ) +
  guides(fill = guide_legend(override.aes =
                               list(size = 0.5),
                             nrow = 1, 
                             byrow = TRUE))

@@

dalys <- data_rev_map %>% 
  filter(measure_id == j) %>% 
  filter(estimate_id %in%  c(1,2,4)) %>% 
  mutate(var_cut = cut(ihme_region_rate_per_100k/1000, 
                       breaks =c(1, 1.5,
                                 2, 2.5, 3, 4, 5, 6, 7, 7.5, 
                                 max(temp$ihme_region_rate_per_100k)/1000))) %>% 
  ggplot() +
  geom_sf(mapping = aes(fill = var_cut), color = "grey95", size = 0.001) +
  geom_sf(data = . %>%   group_by(ihme_region) %>% 
            st_set_precision(1e4) %>%
            summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
  theme(panel.grid.major = element_blank(), 
        panel.background = element_blank(),
        axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        text = element_text(family = "Source Sans Pro")) + 
  labs(subtitle = "A: Disability-adjusted life years",
       fill=
         ifelse(j == 1,ifelse(k == "rate_per_100k", "Deaths", "% of deaths"),
                ifelse(j == 2, ifelse(k == "rate_per_100k", "DALYs, thousands", "% of DALYs"),
                       ifelse(j == 3, ifelse(k == "rate_per_100k", "YLDs, thousands", "% of YLDs"), 
                              ifelse(k == "rate_per_100k", "YLLs, thousands", "% of YLLs"))))) +
  scale_fill_manual(values=setNames(lancet_pal, levels(data_rev_map$var_cut))) +
  coord_sf(ndiscr = F) + 
  facet_grid(~estimate_newlab) +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 11),
        legend.text =  element_text(size = 10),
        plot.subtitle=element_text(size=15),
        text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")
        ,
        strip.text = element_text(size=14)
  ) +
  guides(fill = guide_legend(override.aes =
                               list(size = 0.5),
                             nrow = 1, 
                             byrow = TRUE))

>>>>

# Loading libraries
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(RColorBrewer)
library(sp)
library(broom)
library(sf)
library(scales)
library(viridis)
library(data.table)
library(ggpubr)
library(lemon)
library(rnaturalearth)
library(rnaturalearthdata)
library(sysfonts)
library(showtext)
font_add_google("Source Sans Pro")
library(gridExtra)
showtext_auto() 
showtext_opts(dpi = 300)  
library(rnaturalearthhires) # install.packages("rnaturalearthhires", repos = "http://packages.ropensci.org", type = "source")

col_light = "#b1f2ff"
col_white = "white"
col_black = "black"
col_grey_dark = "grey20"
col_grey_med = "grey40"
col_grey_light = "grey80"
col_grey_lightest = "grey85"
pal <- c("lightskyblue2", "steelblue2", "dodgerblue2", "dodgerblue3", "dodgerblue4", "darkblue")

@@

# Import map data
# world <- ne_countries(scale = "large", returnclass = "sf")
world <- ne_countries(scale = "medium", returnclass = "sf")
world$iso_code <- world$gu_a3
world$iso_code[world$adm0_a3 == "SDS"] <- "SSD"

world$iso_code[world$adm0_a3 == "SOL"] <- "SOM"

world <- world %>%
  group_by(iso_code) %>%
  st_make_valid() %>% 
            summarize(geometry = st_union(geometry))

@@

data_rev$estimate_newlab <- factor(data_rev$estimate_newlab ,      # Reordering group factor levels
                                   levels = c("Original approach",
                                              "Reallocation approach",
                                              "PAF method",
                                              "Composite approach"))
# Merging map and dataframe
data_rev_map <- left_join(world, data_rev, by = "iso_code") %>% filter(numeric_name == "val")

@@

results_sentence1 <- paste0(
  "Under GBD 2019, over ",
  results1,
  " million DALYs were attributed to mental disorders, or roughly ",
  results2,
  "\\% of the global burden. After including alcohol and drug use, neurological disorders, chronic pain, suicide, and self-harm, the share due to mental disorders rose to ",
  results3,
  "\\% of global DALYs (approximately ",
  results4,
  " million DALYs). Under the composite approach, an additional  ",
  abstract1-results4,
  " million DALYs were attributed to mental disorders, encompassing, in total, over ",
  abstract2,
  "\\% of global DALYs (Figure 1). Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising ",
  ifelse(results5/results6 > 2.4, "over twice", ifelse(results5/results6> 2, "roughly twice", "approximately twice")),
  " the burden of disease in high-income countries compared to low-income countries.")

@@

With a third of disability-adjusted life years (DALYs) due to NCDs arising from mental disorders, this landmark paper estimated that the value of losses due to mental disorders was roughly 1.3 trillion USD in 2010 (1.6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion USD 2010 (or approximately 3.0 trillion USD in 2019) by 2030. (See Tables S1.1 and S1.2 in Appendix 1 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]

@@

The most recent estimates of morbidity and mortality due to mental disorders come from the Global Burden of Disease (GBD) 2019 study.[@vosGlobalBurden3692020a] The GBD study provides disease burden estimates using DALYs, years of life lost (YLLs), and years lived with disability (YLDs), which are then aggregated within a hierarchical grouping scheme that classifies causes of disability and death at different levels of mutually exclusive and completely exhaustive categories. (Mental disorders are a Level 2 condition, nested under NCDs; see Table S1.3.)

@@

\addcontentsline{lot}{table}{Table 1.1: Comparison of the composition of the global burden of mental disorders, by estimation approach.}

@@

```
\end{raggedright}

@@

In addition to our base-case economic valuation, we further report our VSL estimates using three times GDP per capita as the value of a DALY. (Alternative valuations using values of $1,000 and $5,000, as well as purchasing power parity (PPP)-adjusted GDP per capita, are reported in Tables S1.5 and S1.6 of Appendix 1)

@@

\blandscape

\addcontentsline{lot}{table}{Table 1.2: Disability-adjusted life years (DALYs) attributable to mental disorders as totals (millions) and percentages of overall burden, by estimation approach.}

```{r table1_2, echo = FALSE, include = TRUE, out.height = '99%'}

@@

@@

Rates of DALYs and deaths attributable to mental disorders under the different estimation approaches are presented by GBD region (Figure \ref{figure_gbd_adjusted}). Geographically, the composite approach allocated a large portion of DALYs (to mental disorders) in Eastern Europe, North and Latin America, and sub-Saharan Africa. This is largely driven by the inclusion of premature mortality in the composite approach. Estimates of DALYs by country income group and GBD region are reported in Table 1.2. (Estimates of deaths are reported in Table S1.4-1.6.)

Under the three approaches, we calculated the economic value of mental disorder losses (Table 1.3). `r results_sentence2`. Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7.2 trillion international dollars in 2019 (Table S1.7).

@@

\blandscape

```{r figure_dalys_nation, include = TRUE, echo = FALSE, warnings = FALSE, fig.scap="DALYs attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.", out.extra='', fig.cap=paste0("\\label{figure_dalys_nation}DALYs attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs. ATG: Antigua and Barbuda; DALYs: disability-adjusted life years; FSM: Federated States of Micronesia; LCA: Saint Lucia; TLS: East Timor; TTO: Trinidad and Tobago; VCT: Saint Vincent and the Grenadines."), fig.width = 13.7, fig.height = 7.5, fig.align='center', out.width = '98%'}

sf_use_s2(FALSE)

data_temporary <- data_rev_map %>% 
  filter(measure_id == 2) %>% 
  filter(estimate_id == 4) %>%
  st_drop_geometry() %>%
  select(iso_code, percent)

world_map <- ne_countries(scale = "large", returnclass = "sf")
# world <- ne_countries(scale = "medium", returnclass = "sf")
world_map$iso_code <- world_map$gu_a3
world_map$iso_code[world_map$adm0_a3 == "SDS"] <- "SSD"
world_map <- left_join(world_map, data_temporary, by = "iso_code")

# First, we make the main map
fun_create_map_helper <- function(data){

  data_temp <- data %>% 
  mutate(var_cut = cut(percent, 
                       breaks =c(0,
                                 6,
                                 7,
                                 8, 
                                 10,
                                 12,
                                 15,
                                 20, 
                                 25, 
                                 30,
                                 35)))

  data_temp %>%
    filter(admin != "Antarctica") %>%
    # group_by(iso_code) %>%
    # st_make_valid() %>% 
    # summarize(geometry = st_union(geometry)) %>%
    # mutate(var_cut = cut(gdp_md_est/1000000, 
    #                      breaks =c(0, 0.1, 0.2, 0.5, 1, 2, 5, 10, 20, 50, 100))) %>%
    ggplot(aes(geometry = geometry, fill = var_cut)) +
    geom_sf(color = col_grey_dark, linewidth = 0.25) +
    scale_fill_manual(values=setNames(lancet_pal, levels(data_temp$var_cut))) +

    # scale_fill_viridis(option = "mako", discrete = TRUE) +
    theme_void()
}

fun_create_map <- function(data, x_1 = -180, x_2 = 180, y_1 = -90, y_2 = 90){

  if(x_1 == -180 &
     x_2 == 180  & 
     y_1 == -90  &
     y_2 == 90 ){

    fun_create_map_helper(data) +
    theme(legend.position = "bottom") +
      labs(fill = "% of DALYs") +
      guides(fill = guide_legend(override.aes =
                                   list(size = 0.5),
                                 nrow = 1, 
                                 byrow = TRUE))

  }else{

    # print(paste0("The x limits of this map are c(",
    #              min(x_1, x_2),", ",
    #              max(x_1, x_2)," and the y limits are c(",
    #              min(y_1, y_2), ", ",
    #              max(y_1, y_2)))

    fun_create_map_helper(data) + theme(legend.position = "",
            panel.border = element_rect(colour = "black", fill = NA, linewidth=.5))   +
      xlim(min(x_1, x_2), max(x_1, x_2)) +
      ylim(min(y_1, y_2), max(y_1, y_2))

  }

}

main_map_upper <- world_map %>%
  fun_create_map()

##### Generate band of countries under neath in blocks

distance <- function(measure, coord1, coord2){

  if(measure == "width"){
    a = coord1[2]
    b = coord2[2]

  }

  if(measure == "height"){
    a = coord1[1]
    b = coord2[1]

  }

  ifelse(a >= 0 & b >= 0, abs(a - b),
         ifelse(a < 0 & b < 0, 
                max(abs(a), abs(b)) - min(abs(a), abs(b)),

                abs(abs(a) + abs(b))))

}

fun_lower_block <- function(country = "all", y1 = -90, x1 = -180, y2 = 90, x2 = 180, 
                            ratio_h_over_w = (0.72/.6), padding = 0.15,
                            nudge = -9, label = country, 
                            text_size = 8, orientation = 0.5){

  if(length(country) == 1){

    if(country == "all")
    {country = world_map$admin}

  }

  coord1 <- c(y1, x1) 
  coord2 <- c(y2, x2)

  # Calculate the width and width of the original rectangle
  width <- distance("width", coord1 = coord1, coord2 = coord2)
  height <- distance("height", coord1 = coord1, coord2 = coord2)

# 
#   print(paste('Height is ', height,
#               "and width is ", width))

  # Determine the center point of the rectangle
  center_lat <- mean(c(coord1[1], coord2[1]))
  center_lon <- mean(c(coord1[2], coord2[2]))

  ratio = height/width

  x1_new = max(x1, x2)
  x2_new = min(x1, x2)
  y1_new = max(y1, y2)
  y2_new = min(y1, y2)

  # print(paste('Midpoint is ', center_lon,
  #             ", ", center_lat,
  #       ". Ratio is ", 
  #       ratio,
  #       ". The target is ",
  #       ratio_h_over_w))

  if (ratio != ratio_h_over_w) {

    # If our ratio is not on target...

    if (ratio > ratio_h_over_w) {

      # and if the height is greater than width, then our figure
      # is too tall, so we will widen our coordinates...

      width_new_half = (height / ratio_h_over_w)/2

      x1_new = center_lon + width_new_half
      x2_new = center_lon - width_new_half

    }

    if (ratio < ratio_h_over_w) {

      # but if the height is less than width, then
      height_new_half = ((width * ratio_h_over_w))/2

      y1_new = center_lat + height_new_half
      y2_new = center_lat - height_new_half

    }

  } else {

    # print("Ratio is perfect!")

  }

  coord1_new <- c(y1_new, x1_new) 
  coord2_new <- c(y2_new, x2_new)

  # Calculate the width and width of the original rectangle
  width <- distance("width", coord1 = coord1_new, coord2 = coord2_new)
  height <- distance("height", coord1 = coord1_new, coord2 = coord2_new)

  # print(paste0("New ratio is ", height/width))

  # print("Making map")

  map <- world_map %>%
    filter(admin %in% country) %>%
    fun_create_map(y_1 = y1_new,  x_1 = x1_new, y_2 = y2_new, x_2 = x2_new) +
    labs(x = label) +
    theme(plot.margin = margin(padding, padding, padding, padding, "cm"),
          panel.border = element_rect(colour = "black", fill = NA, linewidth=.5), 
          axis.title.x =  element_text(size= text_size,
                                       margin = margin(t = nudge),
                                       hjust = orientation),
          text = element_text(family = "Source Sans Pro")

    )
          # ,
          # aspect.ratio=1)

  # print(map)

  return(map)

}

## First block: Caribbean

lower_block_1 <-  fun_lower_block(country = "all",
                                  23.688123201320412, -86.03651405368969,
                                  18.26121082729241, -67.8554147013031, 
                                  label = "Caribbean",
                                  ratio_h_over_w = 2.5/3.35)

## Second block: Islands in Caribbean

lower_block_2_1 <- fun_lower_block("Antigua and Barbuda",  17.78141711279741, -62.2022030527118,
                                   16.79458198479592, -61.39269148570997, label = "ATG")

lower_block_2_2 <- fun_lower_block("Saint Vincent and the Grenadines",
                                     12.391456412985622, -61.60886995955927,
                                     13.419487110651687, -60.88102575796276, label = "VCT")
lower_block_2_3 <- fun_lower_block("Barbados", 13.467115495468354, -59.85117377289456,
                                     12.990476644508814, -59.33382541849154)
lower_block_2_4 <- fun_lower_block("Comoros", -11.24866626955447, 43.00637992019884,
                                     -12.442325445847862, 44.68437738632322)
lower_block_2_5 <- fun_lower_block("Dominica", 15.680375533672533, -61.55835363143402,
                                    15.069402810985572, -61.143539270458746)
lower_block_2_6 <- fun_lower_block("Grenada", 12.54522173412346, -61.87752420403268,
                                     11.883716350869527, -61.371600190809104)
lower_block_2_7 <- fun_lower_block("Maldives", -0.7281644242049007, 73.00822457449168,
                                     -0.5575134138293779, 73.29728811799717)
lower_block_2_8 <- fun_lower_block("Mauritius", -20.620191444040987, 57.15892632861276, 
                                     -19.903825092697055, 58.00959028441021)
lower_block_2_9 <- fun_lower_block("Saint Lucia", 14.16262019208292, -61.164375443799265,
                                     13.539415451808365, -60.76138414727761, label = "LCA")
lower_block_2_10 <- fun_lower_block("Trinidad and Tobago",11.332779122191509, -61.96117584168811,
                                    9.724954484064446, -60.4948421071539, label = "TTO")
lower_block_2_11 <- fun_lower_block("all", -8.055776256847395, 127.5033419027598, 
                                      -10.365527592170913, 123.86686747667004, label = "TLS")

lower_block_2_12 <- fun_lower_block("Seychelles", -4.164500664831933, 55.08971811357248,
                                      -4.87593984585334, 56.013554481127436)

lower_block_2 <- cowplot::plot_grid(lower_block_2_1,
                                    lower_block_2_2,
                                    lower_block_2_3,
                                    lower_block_2_4,
                                    lower_block_2_5,
                                    lower_block_2_6,
                                    lower_block_2_7,
                                    lower_block_2_8,
                                    lower_block_2_9,
                                    lower_block_2_10,
                                    lower_block_2_11,
                                    lower_block_2_12,
                                    rel_heights  = c(1,1,1,1,
                                                   1,1,1,1,
                                                   1,1,1,1),
                                    rel_widths = c(1,1,1,1,
                                                   1,1,1,1,
                                                   1,1,1,1),
                                     # align='h', 
                                     ncol= 4,
                                     axis='t')

# print(lower_block_2)

## Third block:

lower_block_3_1 <-  fun_lower_block(country = "all",
                                    label = "West \nAfrica",
                                    17.55830898122733, -25.766648641326874,
                                    9.591111921718683, -7.308676054124459,
                                    ratio_h_over_w = 0.69/0.95,
                                    nudge = 1)

lower_block_3_2 <-  fun_lower_block(country = "all",
                                    label = "Persian Gulf",
                                    31.578724269583038, 46.68534937362107,
                                    22.201628755387656, 57.91919943035645,
                                    ratio_h_over_w = 1.34/0.89)

lower_block_3_3 <-  fun_lower_block(country = "all",
                                    label = "Eastern \nMediterranean",
                                    35.84337817700235, 32.93408225309256, 
                                    29.953432571862056, 36.94230952794229,
                                    ratio_h_over_w = 0.99/0.82,
                                    nudge = 1) +  theme(aspect.ratio = 1)

lower_block_3_4 <-  fun_lower_block(country = "Malta",
                                    36.11205138041496, 14.109153467789213,
                                    35.749543918885365, 14.641990358572649,
                                    ratio_h_over_w = 0.66/0.82) +  
  theme(aspect.ratio = 1)

lower_block_3_5 <-  fun_lower_block(country = "Singapore",
                                    1.562021407805435, 103.52835737520651, 
                                    1.1508368937798996, 104.17655070980254,
                                    ratio_h_over_w = 0.8/0.82)

lower_block_3a <- cowplot::plot_grid(lower_block_3_1,
                                     lower_block_3_2,

                                     rel_heights  = c(0.99,1.72),
                                     rel_widths = c(1,1),
                                     align='h',
                                     nrow= 2,
                                     axis='t')

lower_block_3b <- cowplot::plot_grid(lower_block_3_3,
                                     lower_block_3_4,
                                     lower_block_3_5,
                                     rel_heights  = c(0.99,
                                                      0.8,
                                                      0.8),
                                     rel_widths = c(1,1,1),
                                     align='h',
                                     nrow= 3,
                                     axis='t')

lower_block_3 <- cowplot::plot_grid(lower_block_3a,
                                    lower_block_3b,
                                    rel_widths =  c(0.89,0.82),
                                    rel_heights = c(1,1),
                                    align='h',
                                    ncol= 2,
                                    axis='t')

# print(lower_block_3)

## Fourth block: Balkans

lower_block_4 <-  fun_lower_block(country = "all",
                                  51.618805792153864, 32.14547175934774, 
                                  35.76671479197162, 12.574073798467166, 
                                  label = "Balkan Peninsula",
                                  ratio_h_over_w = 2.47/2.75) +
  theme(aspect.ratio = 1)

# print(lower_block_4)

## Fifth block: Pacific Islands
lower_block_5_1 <-  fun_lower_block(country = "Marshall Islands",
                                    7.271576767058141, 170.97346175839462,
                                    7.0021405106753924, 171.43254628562116,
                                  label = "Marshall Isl",
                                  ratio_h_over_w = 0.67/0.72)

lower_block_5_2 <-  fun_lower_block(country = "Solomon Islands",
                                    -6.19982314293495, 156.2033043837379,
                                    -12.305942792508677, 162.7810192195895,
                                    label = "Solomon Isl",
                                    ratio_h_over_w = 0.43/0.72)

lower_block_5_3 <-  fun_lower_block(country = "Vanuatu",
                                    -12.522849273606965, 164.09680570696634,
                                    -21.865505295764667, 170.85928793776827,
                                    ratio_h_over_w = 0.43/0.72)

lower_block_5_4 <-  fun_lower_block(country = "Fiji",
                                    -16.016715539187006, 177.43916612705263,
                                    -19.202928284064122, 180,
                                    ratio_h_over_w = 0.55/0.72)

lower_block_5_5 <-  fun_lower_block(country = "Kiribati",
                                    1.6783742083055109, 172.8245591145513,
                                    1.2886789414361417, 173.1873840281737,
                                    ratio_h_over_w = 0.67/0.69)

lower_block_5_6 <-  fun_lower_block(country = "Federated States of Micronesia",
                                    7.123620054481302, 157.66021976354537,
                                    6.527385048863808, 158.46395741107983,
                                    label = "FSM",
                                    ratio_h_over_w = 0.43/0.69)

lower_block_5_7 <-  fun_lower_block(country = "Samoa",
                                   -13.245725830105162, -173.15052189891833,
                                   -14.849661425405092, -171.1345307337241,
                                    ratio_h_over_w = 0.43/0.69)

lower_block_5_8 <-  fun_lower_block(country = "Tonga",
                                    -20.999167868460994, -175.48041913403475,
                                    -21.50983734571705, -174.8335990873945,
                                    ratio_h_over_w = 0.55/0.69)

lower_block_5a <- cowplot::plot_grid(lower_block_5_1,
                                     lower_block_5_2,
                                     lower_block_5_3,
                                     lower_block_5_4,
                                    rel_heights  = c(0.67,0.43,
                                                     0.43, 0.55),
                                    rel_widths = c(1,1,1,1),
                                    align='h',
                                    nrow= 4,
                                    axis='t') 
lower_block_5b <- cowplot::plot_grid(lower_block_5_5,
                                     lower_block_5_6,
                                     lower_block_5_7,
                                     lower_block_5_8,
                                     rel_heights  = c(0.67,0.43,
                                                      0.43, 0.55),
                                     rel_widths = c(1,1,1,1),
                                     align='h',
                                     nrow= 4,
                                     axis='t')

lower_block_5 <- cowplot::plot_grid(lower_block_5a,
                                    lower_block_5b,
                                    rel_widths =  c(0.72,0.69),
                                    rel_heights = c(1,1),
                                    align='h',
                                    ncol= 2,
                                     axis='t')

# print(lower_block_5)

### Joining all blocks together

main_map_lower <- cowplot::plot_grid(lower_block_1,
                                     lower_block_2,
                                     lower_block_3,
                                     lower_block_4,
                                     lower_block_5,
                                     rel_widths = c(3.32,
                                                    3.22,
                                                    1.92,
                                                    2.73,
                                                    1.82),
                                     rel_heights = c(1,1,1,1,1),
                                     align='h', 
                                     ncol=5, 
                                     axis='t')

### Joining upper and lower blocks together

main_map_combined <- cowplot::plot_grid(main_map_upper,
                                        main_map_lower,
                                        rel_heights = c(5.9, 2.8),
                                        rel_widths = c(1,1),
                                        align='v', 
                                        nrow = 2,
                                        axis='l')
main_map_combined

```{r figure_gbd_adjusted, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap="DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population.", out.extra='', fig.cap=paste0("\\label{figure_gbd_adjusted}DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population. Values are aggregated by GBD region. DALYs: Disability-adjusted life years; YLDs: years lived with disability; YLLs: years of life lost; GBD: Global Burden of Disease."), fig.width = 11, fig.height = 11, fig.align='center', out.width = '97%'}

@@

k = "rate_per_100k"

j = 1

@@

deaths <- data_rev_map %>% 
  filter(measure_id == j) %>% 
  filter(estimate_id %in%  c(1,2,4)) %>% 
  mutate(var_cut = cut(ihme_region_rate_per_100k, 
                       breaks =c(0, 1, 20, 40, 60, 80, 100, 120, 130, 140, max(temp$ihme_region_rate_per_100k)))) %>%
  ggplot() +
  geom_sf(mapping = aes(fill = var_cut), color = "grey95", size = 0.001) +
  geom_sf(data = . %>%   group_by(ihme_region) %>% 
            st_make_valid() %>% 
            summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
  theme(panel.grid.major = element_blank(), 
        panel.background = element_blank(),
        axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        text = element_text(family = "Source Sans Pro")) + 
  labs(subtitle = "D: Deaths",
    fill=
      ifelse(j == 1,ifelse(k == "rate_per_100k", "Deaths", "% of deaths"),
             ifelse(j == 2, ifelse(k == "rate_per_100k", "DALYs", "% of DALYs"),
                    ifelse(j == 3, ifelse(k == "rate_per_100k", "YLDs", "% of YLDs"), 
                           ifelse(k == "rate_per_100k", "YLLs", "% of YLLs"))))) +
  scale_fill_manual(values=setNames(lancet_pal, levels(data_rev_map$var_cut))) +
  coord_sf(ndiscr = F) + 
  facet_grid(~estimate_newlab) +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 11),
        legend.text =  element_text(size = 10),
        plot.subtitle=element_text(size=15),
        text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")
        ,
        strip.text = element_text(size=14)
  ) +
  guides(fill = guide_legend(override.aes =
                               list(size = 0.5),
                             nrow = 1, 
                             byrow = TRUE))

@@

dalys <- data_rev_map %>% 
  filter(measure_id == j) %>% 
  filter(estimate_id %in%  c(1,2,4)) %>% 
  mutate(var_cut = cut(ihme_region_rate_per_100k/1000, 
                       breaks =c(1, 1.5,
                                 2, 2.5, 3, 4, 5, 6, 7, 7.5, 
                                 max(temp$ihme_region_rate_per_100k)/1000))) %>% 
  ggplot() +
  geom_sf(mapping = aes(fill = var_cut), color = "grey95", size = 0.001) +
  geom_sf(data = . %>%   group_by(ihme_region) %>% 
            st_make_valid() %>% 
            summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
  theme(panel.grid.major = element_blank(), 
        panel.background = element_blank(),
        axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        text = element_text(family = "Source Sans Pro")) + 
  labs(subtitle = "A: Disability-adjusted life years",
       fill=
         ifelse(j == 1,ifelse(k == "rate_per_100k", "Deaths", "% of deaths"),
                ifelse(j == 2, ifelse(k == "rate_per_100k", "DALYs, thousands", "% of DALYs"),
                       ifelse(j == 3, ifelse(k == "rate_per_100k", "YLDs, thousands", "% of YLDs"), 
                              ifelse(k == "rate_per_100k", "YLLs, thousands", "% of YLLs"))))) +
  scale_fill_manual(values=setNames(lancet_pal, levels(data_rev_map$var_cut))) +
  coord_sf(ndiscr = F) + 
  facet_grid(~estimate_newlab) +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 11),
        legend.text =  element_text(size = 10),
        plot.subtitle=element_text(size=15),
        text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")
        ,
        strip.text = element_text(size=14)
  ) +
  guides(fill = guide_legend(override.aes =
                               list(size = 0.5),
                             nrow = 1, 
                             byrow = TRUE))
